Climate indicators

### 2023-03-03 DRAFT_climate_indicators.Rmd
map with regions

```{r, eval=T}
names(real_temp_summer)
```

```{r, eval=T}
dim(real_temp_summer)
```

```{r, eval=T}
st_get_dimension_values(real_temp_summer, "Year")
```

@@

That was fast! 
```{r}
regional_means
```

@@

@@

```{r}
reg2 <- reg %>%
  left_join(i_aggregatedToPeriods[i_aggregatedToPeriods$period_rank==5,], by=join_by(region))

```{r}
ggplot(reg2) + 
  geom_sf(fill = indicator) +
  geom_sf_label(aes(label = indicator))

```{r}
tm_shape(reg2)+
  tm_polygons(col=)
```

>>>>

```{r, eval=T}
names(temp_median_summer)
```

```{r, eval=T}
dim(temp_median_summer)
```

```{r, eval=T}
st_get_dimension_values(temp_median_summer, "Year")
```

@@

That was fast!

@@

```{r}
regional_means
```

@@

```{r}
reg2 <- reg %>%
  left_join(i_aggregatedToPeriods[i_aggregatedToPeriods$period_rank==5,], by=join_by(region))
names(reg2)
```

```{r}
myCol <- "RdYlGn"
myCol2 <- "-RdYlGn"

tm_main <- tm_shape(reg2)+
  tm_polygons(col="indicator",
              title="Indikator:\nsommertemperatur",
    palette = myCol,
    style="fixed",
    breaks = seq(0,1,.2))

tm_inset <- tm_shape(reg2)+
  tm_polygons(col="spatial_sd",
              title="SD",
              palette = myCol2,
              style="cont")+
  tm_layout(legend.format = list(digits=2))

#tm_main <- tmap_grob(tm_main)
#tm_inset <- tmap_grob(tm_inset)

#ggdraw() +
#  draw_plot(tm_main) +
#  draw_plot(tm_inset,
#    height = 0.4,
#    x = 0.12, y = .35
#  )

tmap_arrange(tm_main, 
             tm_inset)
```
